### 2020-07-19 paper.tex
add acks

%\subsubsection*{Acknowledgements}

>>>>

\subsubsection*{Acknowledgements}
This research was supported in part by the US Department of Defense through the the National Defense Science \& Engineering Graduate Fellowship (NDSEG) Program, the DARPA SD2 program (contract FA8750-17-C-0239), the DARPA Machine Common Sense (MCS) program, the DARPA Synergistic Discovery and Design (SD2) program, support from the Intel Corporation, and a philanthropic gift from the Aphorism Foundation.
The authors would also like to thank Feras Saad and Cameron Freer for helpful discussions.
